White Dwarf Mergers on Adaptive Meshes\\ I. Methodology and Code Verification

### 2015-09-22 papers/wdmerger_I/paper.tex
Updated strategy for tagging

The computational domain has a total size of $1.024 \times
10^{10}\ \text{cm}$ in each spatial dimension, and is centered at the
origin. Our coarse grid has $256^3$ zones, corresponding to a spatial
resolution of 400 km. For the present study, we choose a simple
refinement strategy: all zones within twice the Roche radius of each
star are tagged for maximal refinement. The extra buffer from doubling
the size of this region ensures that the sharp density gradients near
the edge of the star are within the zone of refinement. We also ensure
that the outer part of the domain is never tagged for refinement. In
future work we will add criteria that tag for refinement the gas
between the stars, which is expected to feature nuclear burning.

>>>>

The computational domain has a total size of $1.024 \times
10^{10}\ \text{cm}$ in each spatial dimension, and is centered at the
origin. Our coarse grid has $256^3$ zones, corresponding to a spatial
resolution of 400 km. For the present study, we choose a simple
refinement strategy: on the coarse grid, all zones within twice the Roche radius of each
star are tagged for refinement. The extra buffer from doubling
the size of this region ensures that the sharp density gradients near
the edge of the star are within the zone of refinement. On higher levels, 
we tag all zones above a given density threshold (taken to be $1\ \text{g cm}^{-3}$ 
in this paper) that corresponds to the stars themselves. We also ensure
that the outer part of the domain is never tagged for refinement. In
future work we will add criteria that tag for refinement the gas
between the stars, which is expected to feature nuclear burning.
